---
title: "Statistiek I - Lab session 1"
author: "Robert van Timmeren (s4535553)"
date: "Generated on: `r date()`"
output: 
  html_document:
    toc: true
    code_folding: show
    toc_float: 
        collapsed: false
        smooth_scroll: true
    number_sections: true
---

# Exercise 1


```{r, fig.width=5, fig.height=5}
# R code for this exercise goes between the ```'s 
# Lines which start with a '#' are comments and not executed.
# Remove the '#' at the start of the next line and press the Knit HTML button
R.version.string

# Reading the data file 'data.csv' and then showing its data structure.
dat <- read.csv('data.csv',sep=';',dec='.')
str(dat)
```

The `read.csv` command reads the provided .csv file given in its parameter into R, which can then be stored in a variable. Additional parameters are possible/required, for instance, to define seperation of values and what decimal seperation is used.


# Exercise 2

```{r, fig.width=5, fig.height=5}
# Changes the participant column type from int to factor with 50 levels and then checks this.
dat$participant <- as.factor(dat$participant)
str(dat)
```


# Exercise 3

```{r, fig.width=5, fig.height=5}
#Calculates the mean of the column english_grade.
mean(dat$english_grade)

#Calculates the mean of english_grade for only men.
mean(dat[dat$gender== "M", ] $english_grade)

#Creates a cross table of gender and study.
table(dat$gender, dat$study)
```

I definitely think there is a relation between gender and study. It seems that IS is a study that is mainly male dominated, whereas Ling is mainly female dominated. The data for CIS and others studies doesn't seem to be sufficient enough to really formulate any conclusions.


# Exercise 4

```{r, fig.width=5, fig.height=5}
#Creates and shows a frequency table that shows the distribution of male and female and stores it in variable called gendertable.
gendertable <- table(dat$gender)
gendertable

#Creates and shows a frequency table that shows the distribution of whether someone followed a bilingual education.
bltable <- table(dat$bl_edu)
bltable

#Creates a barplot that shows the distribution of the genders of the respondents.
barplot(gendertable, col = c("pink", "lightblue"), ylim = c(0, 40), main="Distribution female and male respondents", xlab="Gender", ylab="Frequency")

#Creates a barplot that shows the distribution of whether a person followed a bilingual education.
barplot(bltable, col = c("firebrick1", "lightgreen"), ylim = c(0, 50), main="Distribution followed bilingual education", xlab="Answer", ylab="Frequency")

